Examining Programming Students’ Interaction with Generative AI: A Metacognitive Perspective

### 2024-10-16 CSEDU2025/Paper.tex
update data

Figure \ref{fig:graph1} also shows that around 5\% of the prompts written by
students were not categorized. These messages range from greetings to the Bot,
such as a simple "\textit{Hello}," to contextual statements like
"\textit{I'm reviewing object orientation}"

>>>>

Figure \ref{fig:graph1} also shows that around 5\% of the prompts written by
students were not categorized. These messages range from gratitude to the Bot,
such as a simple "\textit{thanks}," to contextual statements like
"\textit{I'm reviewing object orientation}"
